---
title: "Project"
format: html
editor: visual
---

## Data Description

I have used a dataset called Salary Data available on Kaggle. The data contains two variables: (1) Years of experience of employees (x); (2) Salary (y). The aim is to predict Salary using Linear Models.

```{r}
library(skimr)
library(caTools)
data <- read.csv('/Users/sakshardesai/Downloads/Salary_Data.csv')
skim(data)
```

## Data Visualization

```{r}
x <- data$YearsExperience
y <- data$Salary
plot(x,y)
```

## Simple Linear Regression

```{r}
sample <- sample.split(data$YearsExperience, SplitRatio = 0.7)
train  <- subset(data, sample == TRUE)
test   <- subset(data, sample == FALSE)
x_train <- train$YearsExperience
x_test <- test$YearsExperience
y_train <- train$Salary
y_test <- test$Salary
x_new <- (x_train-mean(x_train))/sd(x_train)
y_new <- (y_train-mean(y_train))/sd(y_train)
slr <- lm(y_new~x_new)
summary(slr)
plot(x_new,y_new)
abline(slr)
```

## Quadratic Regression

```{r}
x2 <- x_train^2
x2_new <- (x2-mean(x2))/sd(x2)
qr <- lm(y_new~x_new+x2_new)
summary(qr)
```

## Prediction

```{r}
x2_test <- x_test^2
x_test <- (x_test-mean(x_test))/sd(x_test)
x2_test <- (x2_test-mean(x2_test))/sd(x2_test)
y_test <- (y_test-mean(y_test))/sd(y_test)
pred_slr <- predict(slr,newdata = data.frame(x_new = x_test))
pred_qr <- predict(qr,newdata = data.frame(x_new=x_test,x2_new=x2_test))
mean((pred_slr-y_test)^2)
mean((pred_qr-y_test)^2)
```

## Discussion

The simple linear regression model shows slightly better prediction accuracy than the quadratic regression model. Moreover, the quadratic coefficient is not significant as seen from the summary table of quadratic model.
